|

### 2024-12-20 output/sandbox_slideshow.qmd
Add probability axis elements for unidimensional representation
Add item palette to sandbox slide

```{r pre}
PROB_AXIS_2D <- seq(-3, 3, by = .1)
F1_COLOR <- unname(PALETTE_BLUE["normal"])

@@

```

>>>>

```{r pre}
PROB_AXIS    <- seq(-3, 3, by = .01)
ERROR_POINTS <- seq(-3, 3, length.out = 5)
PROB_AXIS_2D <- seq(-3, 3, by = .1)
F1_COLOR <- unname(PALETTE_BLUE["normal"])

@@

ITEMS_PALETTE <- c(
  PALETTE_BLUE["normal"],
  PALETTE_RASPBERRY["normal"],
  PALETTE_APPLE["normal"],
  PALETTE_TANGERINE["normal"]
) |>
  unname() |>
  setNames(paste(1:4, sep = '_'))
```
